Collaborative Visual Analysis with RCloud

### 2015-08-17 casestudies.tex
back to 8 pages. do not peek into the patch lest you'd like a lesson in sausagemaking

\begin{figure*}
  \includegraphics[width=\linewidth]{fig/casestudytext/casestudytext.pdf}
  \caption{\label{fig:textvis}The Topic Model Web Tool (TMWT), an example application developed
    and deployed entirely in RCloud.  TMWT allows analysts to
    fit and visually explore \emph{topic models}, statistical
    representations of different topics in a document collection.
  }
\end{figure*}

@@

Each topic under LDA is a probability distribution over the all the unique
words in the collection of documents. To expose patterns in the relationships
between topics, LDAVis combines
interactive visualization and dimensionality reduction,
allowing users to adjust measures for topic distances and the choice
of dimensionality reduction technique. The dimensionality reduction
algorithms and distance measures are implemented in R, which
means they can be executed on RCloud servers as well.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=.85\linewidth]{fig/casestudytext/casestudytext.pdf}
  \vspace{-1em}
  \caption{\small \label{fig:textvis}The Topic Model Web Tool (TMWT), an example application developed
    and deployed entirely in RCloud.  TMWT allows analysts to
    fit and visually explore \emph{topic models}, statistical
    representations of different topics in a document collection.
  }
  \vspace{-1.5em}
\end{figure*}

@@

Each topic under LDA is a probability distribution over all the unique
words in the collection of documents. To expose patterns in the relationships
between topics, LDAVis combines
interactive visualization and dimensionality reduction,
allowing users to adjust measures for topic distances and the choice
of dimensionality reduction technique. The dimensionality reduction
algorithms and distance measures are implemented in R, which
means they can be executed on RCloud servers as well.

### 2015-08-17 paper.tex
Fixed author locations
back to 8 pages. do not peek into the patch lest you'd like a lesson in sausagemaking

\documentclass[journal]{vgtc}                % final (journal style)
%\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)
%\documentclass[electronic,journal]{vgtc}     % electronic version, journal

@@

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
\usepackage{xspace}
\usepackage{amssymb}
\newcommand{\comment}[1]{}

@@

%% This turns references into clickable hyperlinks.
\usepackage[bookmarks,backref=true,linkcolor=black]{hyperref} %,colorlinks
\hypersetup{
  pdfauthor = {},
  pdftitle = {},
  pdfsubject = {},
  pdfkeywords = {},
  colorlinks=true,
  linkcolor= black,
  citecolor= black,
  pageanchor=true,
  urlcolor = black,
  plainpages = false,
  linktocpage
}

%% If you are submitting a paper to a conference for review with a double
%% blind reviewing process, please replace the value ``0'' below with your
%% OnlineID. Otherwise, you may safely leave it at ``0''.
\onlineid{341}

%% declare the category of your paper, only shown in review mode
\vgtccategory{Research}

%% allow for this line if you want the electronic option to work properly
\vgtcinsertpkg

@@

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Stephen North, Carlos Scheidegger, Simon Urbanek and
  Gordon Woodhull}

\authorfooter{
%% insert punctuation at end of each item
\item 
Stephen North is with Infovisible LLC, Oldwick, USA, and graphviz.org.
\\Email: s.c.n@ieee.org
\item
Carlos Scheidegger is with the University of Arizona, USA.
\\Email: cscheid@email.arizona.edu
\item
Simon Urbanek is with AT\&T Labs in Bedminster, USA.
\\Email: urbanek@research.att.com
\item
Gordon Woodhull is with AT\&T Labs in Bedminster, USA.
\\Email: gordon@research.att.com
}

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.80\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{
An overview of features in RCloud.
RCloud is an environment in which \emph{hackers} and \emph{scripters}
solve problems in data and visual analytics and create web applications
and services.  It is a shared environment, in which \emph{discoverability} is a concern.
RCloud supports search, annotation, recommendation, and commenting for all notebooks, and provides an overview where users can \emph{browse} popular and recent analyses. When problems and data sources change frequently, deployment can become very costly; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from data exploration to production.
  }
% \vspace{-.5em}
}

>>>>

\documentclass{vgtc}                % final (journal style)
\let\ifpdf\relax
%\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)
%\documentclass[electronic,journal]{vgtc}     % electronic version, journal

@@

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{amssymb}
\newcommand{\comment}[1]{}

\usepackage{times}

@@

%% This turns references into clickable hyperlinks.

%% If you are submitting a paper to a conference for review with a double
%% blind reviewing process, please replace the value ``0'' below with your
%% OnlineID. Otherwise, you may safely leave it at ``0''.

%% declare the category of your paper, only shown in review mode

%% allow for this line if you want the electronic option to work properly

@@

\linespread{0.9575} % I hate myself

@@

%% indicate IEEE Member or Student Member in form indicated below
\author{Stephen North \thanks{e-mail: s.c.n@ieee.org}\\ %
  \scriptsize Infovisible %
  \and Carlos Scheidegger \thanks{e-mail: cscheid@cs.arizona.edu}\\ %
  \scriptsize University of Arizona %
  \and Simon Urbanek\thanks{e-mail: urbanek@research.att.com}\\ %
  \scriptsize AT\&T Labs %
  \and Gordon Woodhull\thanks{e-mail: gordon@research.att.com}\\ %
  \scriptsize AT\&T Labs}

%% \authorfooter{
%% %% insert punctuation at end of each item
%% \item 
%% Stephen North is with Infovisible, Oldwick, USA, and graphviz.org.
%% \\Email: s.c.n@ieee.org
%% \item
%% Carlos Scheidegger is with the University of Arizona, USA.
%% \\Email: cscheid@email.arizona.edu
%% \item
%% Simon Urbanek is with AT\&T Labs in Bedminster, USA.
%% \\Email: urbanek@research.att.com
%% \item
%% Gordon Woodhull is with AT\&T Labs in New York, USA.
%% \\Email: gordon@research.att.com
%% }

@@

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.70\linewidth]{fig/teaser/teaser.pdf}
  % \vspace{-.5em}
  \caption{ \small
An overview of features in RCloud.
RCloud is an environment in which \emph{hackers} and \emph{scripters}
solve problems in data and visual analytics and create web applications
and services.  It is a shared environment, in which \emph{discoverability} is a concern.
RCloud supports search, annotation, recommendation, and commenting for all notebooks, and provides an overview where users can \emph{browse} popular and recent analyses. When problems and data sources change frequently, deployment can become very costly; RCloud supports \emph{transparent and automatic} deployment of analyses as web pages and web services, allowing a seamless transition from data exploration to production.
  }
 \vspace{-1.5em}
}
